Brief Announcement: An Improved Lower Bound for Dynamic Balanced Graph Partitioning

### 2020-02-16 paper/paper.tex
Preliminaries and consistency check
Fixed one of the crucial paragraphs in k=3

@@

  \maciek{Rewrite the paragraph to emphasize in the definition that requests that did not increase the counter are not included}
  We distinguish two disjoint subsequences of input $\sigma$ that arrived during the phase: $\sigma_I$ and $\sigma_E$, called \emph{internal} and \emph{external}, respectively.
  We only account for the requests to nodes that were not collocated by \TAlg at the moment of their arrival, i.e., the requests that increased a counter.
  The subsequence $\sigma_E$ contains requests to pairs that belong to the same component of \TAlg{} at the end of the phase, and $\sigma_I$ denotes the requests to pairs that did not belong to the same component of \TAlg.

>>>>

\section{Preliminaries}

\maciek{if preliminaries are short, we should merge them with the previous section}

An algorithm that  keeps all components collocated is \emph{component-respecting}.

\maciek{external requests}

@@

  In our analysis, we use two disjoint subsequences of input $\sigma$ that arrived during the phase: $\sigma_I$ and $\sigma_E$.
  Let $\sigma'$ be the requests that at the moment of arrival were external requests for \TAlg.
  The sequence $\sigma_I$ (inter-component requests) are the requests from $\sigma'$ issued to pairs that belong to the same component of \TAlg at the end of the phase.
  The sequence $\sigma_E$ (extra-component requests) are the requests from $\sigma'$ issued to pairs that did not belong to the same component of \TAlg at the end of the phase.
